Considering scale in multilayer animal social networks

### 2020-06-14 paper/manuscript.Rmd
consistent "time window"

Increasing land cover resolution resulted in a decreased availability of forage,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap was relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
forage layers across land cover resolutions than open and forest (Figure
\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in forage habitat
(Supp. 1 <!-- todo-->).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

@@

The ordinal multilayer network generated from discrete time windows indicate
within-year periods of increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and 15-20 than time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). These periods between approximately October and May

increasing graph strength with overall peak in 2018 but still increases in 2019
note graph connectedness is evident panel B

<!-- Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.  -->
These
results suggest that an increasing window length, especially for the summer
season, may be resulting in less precisely defined seasons that are not clearly
capturing periods of aggregation and dissaggregation related to resource
availability.

changing the position of the
time window in this case results in a mismatch between expected periods of
resource seasonality and corresponding sociality, particularly for the summer,
highlighting the importance of carefully selecting temporal scale of analysis.

>>>>

Increasing land cover resolution resulted in decreased availability of forage,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
forage layers across land cover resolutions than open and forest (Figure
\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in forage habitat
(Supp. 1 <!-- todo-->).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

@@

The ordinal multilayer network generated indicated
within-year time windows of increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and 15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between approximately October and May, had correspondingly higher graph strength compared to time windows of lower edge overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time series in periods 9 and 10. These results suggest that ordinal multilayer networks
can effectively capture discrete time windows of aggregation and dissaggregation related to resource availability, and highlight the importance of carefully selecting the temporal scale of analysis.
